---
title: "Hands-on Exercise 4"
author: "Law Shiang Rou"
date: 3 February 2023
date-modified: "`r Sys.Date()`"
execute: 
  echo: true
  eval: true
  warning: false
format: html
editor: visual
---


# Loading required packages
```{r}
pacman::p_load(ggstatsplot, tidyverse)
```

# Importing data
```{r}
exam <- read_csv("data/Exam_data.csv")
```

# One-sample test: gghistostats() method
Use gghistostats() to build a visual of one-sample test on English scores.
```{r}
set.seed(1234)

gghistostats(
  data = exam,
  x = ENGLISH,
  type = "bayes",
  test.value = 60,
  xlab = "English scores"
)
```

# Two-sample mean test: ggbetweenstats()
Use ggbetweenstats() to build a visual for two-sample mean test of Maths scores by gender.
```{r}
ggbetweenstats(
  data = exam,
  x = GENDER, 
  y = MATHS,
  type = "np",
  messages = FALSE
)
```

# Oneway ANOVA Test: ggbetweenstats() method
Use ggbetweenstats() to build a visual for One-way ANOVA test on English score by race.
```{r}
ggbetweenstats(
  data = exam,
  x = RACE, 
  y = ENGLISH,
  type = "p",
  mean.ci = TRUE, 
  pairwise.comparisons = TRUE, 
  pairwise.display = "s",
  p.adjust.method = "fdr",
  messages = FALSE
)
```

# Significant Test of Correlation: ggscatterstats()
Use ggscatterstats() to build a visual for Significant Test of Correlation between Maths scores and English scores.
```{r}
ggscatterstats(
  data = exam,
  x = MATHS,
  y = ENGLISH,
  marginal = FALSE,
  )
```

